% ------------------------------------------------------------------------------
% Packages descritions.
%
% @file     packages.tex
% @author   Éric Poirier
% @date     May 2019
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
% Copyright (C) 2019 Connect X team.
%
% This file is part of Connect X.
%
% Connect X is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% Connect X is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Connect X.  If not, see <http://www.gnu.org/licenses/>.
% ------------------------------------------------------------------------------

% Packages descriptions:
\newcommand{\cxinvDescription}{Utilities to check that some system conditions
are respected. These utilities include various assertions macros, such a
basic assertion, preconditions, postconditions, invariants, and so on.}

\newcommand{\cxmathDescription}{Mathematical tools are stored in this package.
They include, points, vectors and many operations on these. Most of the tools
are generic.}

\newcommand{\cxutilDescription}{General utilities that either have no place in
any other packages. These often include very basic utilities, such as the
\ttt{narrow\_cast} function, which has no logical binding to any other package.}

\newcommand{\cxcmdDescription}{Regroups everything that is nedded to create
command objects, from a command interface to an undo stack. Note that the
concrete commands themselves are not created here. This package only handles
the abstract command utilities.}

\newcommand{\cxbaseDescription}{Contains all the buisness rules. In other words,
every piece of logic \textit{directly} related to a \connectx game is
in this package. It is the core of the application.}

\newcommand{\cxosDescription}{Contains abstractions over the operating system.}

\newcommand{\cxlogDescription}{Regroups logging utilities.}

\newcommand{\cxguiDescription}{Contains reusable GUI components (i.e, components
that could be reused in another application entirely). No \connectx GUI
components should reside in this package.}

\newcommand{\cxexecDescription}{All \connectx specific code is located here.
This package is the least reusable of all.}


Every \connectx package is described here:

\begin{description}
    \item[\cxinv]   \cxinvDescription
    \item[\cxmath]  \cxmathDescription
    \item[\cxutil]  \cxutilDescription
    \item[\cxcmd]   \cxcmdDescription
    \item[\cxbase]  \cxbaseDescription
    \item[\cxos]    \cxosDescription
    \item[\cxlog]   \cxlogDescription
    \item[\cxgui]   \cxguiDescription
    \item[\cxexec]  \cxexecDescription
\end{description}
