% ------------------------------------------------------------------------------
% Connect X project's programming standard style section.
%
% This document discusses style issues, that is, how to format names and 
% such.
%
% @file     style.tex
% @author   Éric Poirier
% @date     March, 2017
% @version  1.1
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
% Copyright (C) 2017 Connect X team.
%
% This file is part of Connect X.
%
% Connect X is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% Connect X is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Connect X.  If not, see <http://www.gnu.org/licenses/>.
% ------------------------------------------------------------------------------

\section{Identation}
  Allman's ident style was chosen for this project because of its clarity. 
  This style puts the brace associated with a control statement on the next 
  line, indented to the same level as the control statement. Statements within 
  the braces are indented to the next level.
  
  \includecode{\styleSnippets indentationAllman.cpp}
  
  \clearpage
  
  From Wikipedia:
  
  \begin{quote}
  Consequences of this style are that the indented code is clearly set apart 
  from the containing statement by lines that are almost completely whitespace 
  and the closing brace lines up in the same column as the opening brace. Some 
  people feel this makes it easy to find matching braces. The blocking style 
  also delineates the actual block of code from the associated control 
  statement itself. Commenting out the control statement, removing the control 
  statement entirely, refactoring, or removing of the block of code is less 
  likely to introduce syntax errors because of dangling or missing braces. 
  Furthermore, it's consistent with brace placement for the outer/function 
  block.\cite{noauthor_indent_2017}
  \end{quote}

\section{Naming format conventions}

The various formats presented here aim at marking a clear distinction between 
any piece of code used. They bring further distinctions among types of code 
structures and help avoid errors.

\subsection{Variables}

% Standard variables:
Variables need to follow a \texttt{camelCase} format:

\includecode{\styleSnippets variables.cpp}

% Constants:
Constant need to be in \texttt{UPPERCASE} format. If you want separate words 
in a constant name, only the underscore (\_) character is allowed, as in 
\texttt{UPPERCASE\_CONSTANT}:

\newpage

\includecode{\styleSnippets constants.cpp}

% Parameters:
To differentiate parameters from regular variables or member variables, the 
prefix \texttt(p\_) has to be added before the parameter variable name (which 
should be in \texttt{camelCase}. In other words, the format is 
\texttt{p\_myParameter}:

\includecode{\styleSnippets parameters.cpp}

% Attributes:
Like parameters, member variables often need to be distinguished from other 
variables, including parameters. The prefix \texttt{m\_} needs to be added 
befor the variable name (in \texttt{camelCase}). The format is: 
\texttt{m\_memberVariable}:

\includecode{\styleSnippets attributes.cpp}

Notice in the last code snippet ---in the constructor's initialization list--- 
how the parameter/member variable distinction is clear.

\subsection{Functions and methods}
Function and method names follow the same rules as variables, that is they are 
written in \texttt{camelCase}. Of course, constructors and destructors are 
exceptions of this.

  \newpage

  \includecode{\styleSnippets functionsAndMethods.cpp}

\subsection{MACROs}
MACRO names follow the same rules as constants, that is they are written in 
\texttt{UPPERCASE}, possibly with underscores between seperated words. MACRO 
parameters, however, do not follow the same conventions as regular parameters. 
Rather, the format \texttt{\_\_parameterName\_\_} is used. These two rules 
combined make it very clear that the piece of code used is not a function or a 
method, but a MACRO.

  \includecode{\styleSnippets macros.cpp}

\subsection{Classes, structures and enumerations}

% Naming
A class name uses the \texttt{CamelCase} format. They always start with an 
uppercase letter. If more than one word is used to describe the class, 
uppercase letters for every first letter of a word are used to distinguish 
them. This helps avoid confusion between a class name and an instance name.

  \includecode{\styleSnippets classesAndStructs.cpp}
  
% Access
To avoid confusion, respect the following order for member access when 
declaring an class interface:
\begin{enumerate}
 \item \texttt{public};
 \item \texttt{protected};
 \item \texttt{private}.
\end{enumerate}
Sometimes, this rule is hard to follow. When not possible, duplicate as 
few access keyword as possible throughout the class interface.

  \includecode{\styleSnippets classAccess.cpp}
  
% Interfaces
Interface classes names follow the same pattern as regular classes, but an 
'\texttt{I}' character is added before the name. The pattern is 
\texttt{IClass}: 

  \includecode{\styleSnippets interfaces.cpp}
  
% Enumerations
Enumerations follow the same naming convention as regular classes. The actual 
enumeration can take place on one single line, but can also span on several 
lines if the layout seems clearer:

  \includecode{\styleSnippets enums.cpp}
  
% Test classes
A class that is tested using another class (for example by creating a test 
fixture in Google Tests) should always hold the original class name followed by 
the string \texttt{Tests}, clearly identifying its purpose. The format is 
\texttt{ClassTests}:

  \includecode{\styleSnippets testClasses.cpp}
  
\subsection{Files}

A class should be interfaced in an eponym header file and implemented in an 
eponym source file. The class should be tested in a source file whose 
name begins with \texttt{test\_} and ends with the class name. In other words:

\begin{center}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Item}  & \textbf{Name format}  \\
    \hline\hline
    class          & \texttt{Foo}          \\
    header file    & \texttt{Foo.h}        \\
    source file    & \texttt{Foo.cpp}      \\
    test file      & \texttt{test\_Foo.cpp} \\
    \hline
  \end{tabular} 
\end{center}

\clearpage

  \includecode{\styleSnippets files.cpp}

The only file extensions accepted are \texttt{.h} and \texttt{.cpp} for 
uniformity. These extensions are supported by nearly all compilers.

\clearpage

\subsection{Namespaces}

Namespace names should always be composed of a couple lowercase letters and 
possibly numbers. They are candidates to be typed often by the programmer 
and hence should not exceed six (6) characters in order not to become a burden. 
For example, the Standard Template Library uses the namespace \ttt{std} for 
its members.

Furthermore, it is good practice to use a \ttt{\#define} to hide the namespace 
name. This way, if the namespace name changes (idealy, it should not), the 
program can sucessfully recompile with almost no work. For example, this is 
a set of \ttt{\#define}s used for the Standard Template Library:

  \includecode{\styleSnippets namespaceMacro.cpp}

You can then use namespaces in the following manner in your code:

  \includecode{\styleSnippets namespaceUse.cpp}

The idea is to be consistent at least within a same module, and ideally across 
the whole code base.

\subsection{Summary}

The \cref{tblNamingConventions} summarizes all naming conventions introduced in 
this section.

\begin{table}[H]
  \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Item}              & \textbf{Format}                            \\
    \hline\hline
    variable                   & \ttt{camelCase}                            \\
    constant                   & \ttt{UPPERCASE\_CONSTANT}                  \\
    parameter                  & \ttt{p\_camelCase}                         \\
    member variable            & \ttt{m\_camelCase}                         \\
    function \& method         & \ttt{camelCase()}                          \\
    MACRO (w/o param)          & \ttt{UPPERCASE\_MACRO()}                   \\
    MACRO (param)              & \ttt{UPPERCASE\_MACRO(\_\_aParameter\_\_)} \\
    class                      & \ttt{CamelCase}                            \\
    structure                  & \ttt{CamelCase}                            \\
    enumeration                & \ttt{CamelCase}                            \\
    interface                  & \ttt{ICamelCase}                           \\
    files                      & \ttt{[test\_]CamelCase[.h/.cpp]}           \\
    namespace                  & \ttt{namesp} (6 chars max.)                \\
    \hline
  \end{tabular} 
  \caption{Summary of the naming conventions}
  \label{tblNamingConventions}
\end{table} 

\section{Spacing}

The only spacing rule is to respect a \textbf{150 characters limit} for every
line of code.