% ------------------------------------------------------------------------------
% Connect X project's programming standard section on methods and functions.
%
% This sections explains how to use functions and methods.
%
% @file     functions.tex
% @author   Éric Poirier
% @date     March, 2017
% @version  1.1
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
% Copyright (C) 2017 Connect X team.
%
% This file is part of Connect X.
%
% Connect X is free software: you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation, either version 3 of the License, or
% (at your option) any later version.
%
% Connect X is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with Connect X.  If not, see <http://www.gnu.org/licenses/>.
% ------------------------------------------------------------------------------

The following sections apply both to methods and (free) functions.

\section{Parameter passing}
Parameters, when they represent objects (custom or not) should always be passed 
as references to avoid uneccessary copying. In other words, a parameter named 
\ttt{p\_aParameter} of type \ttt{Object} should be passed as:

\begin{center}
\ttt{Object\& p\_aParameter}.
\end{center}

if the object referred to by \ttt{p\_aParameter} is assumed to see it's value 
modified (usually an out parameter) or

\begin{center}
\ttt{const Object\& p\_aParameter}.
\end{center}

if the object is assumed not to change. If the parameter is of a fundamental 
data type and is not an object (\ttt{int}, \ttt{bool}, \ttt{double}, etc), 
this rule does not apply since copy is cheap. For example:

\includecode{\functionsSnippets parameters.cpp}

\section{\ttt{const} correctness}
\ttt{const} correctness is perhaps one of the most important rules introduced 
in this document. If a method does not modify the object it acts upon, mark it 
as \ttt{const}. Consider the following example:

\includecode{\functionsSnippets const.cpp}
which shows how \ttt{const} correctness helps avoid tricky mistakes by running 
checks at compile time!

\section{Other specifiers}
The \ttt{delete} keyword should be added to methods which should not exist in a 
class (usually because they don't make sense in the context of the class). For 
example, in the class \ttt{Person} below, the programmer has decided that 
instanciating am object without specifying a name should not be done. 
Therefore, he deleted the default constructor:

\includecode{\functionsSnippets delete.cpp}

The \ttt{override} keyword is also very important. The following example shows 
how it can be used to avoid errors using the compiler:
\includecode{\functionsSnippets override.cpp}

In this case, the \ttt{override} addition makes the compiler complain that the 
method with the signature

\begin{center}
 \ttt{int foo();}
\end{center}
does not exist in the base class. This tells the programmer that the 
\ttt{const} keyword is absent from the signature instead of generating a "new" 
non \ttt{const} \ttt{foo()} method (Notice in the example how the keyword 
\ttt{virtual} is repeated in the overriden method signature. This is good 
practice!).

These two keywords should always be used, when applicable.

Other keywords such as \ttt{default} and \ttt{final} can be used but are not 
mandatory.

\section{Virtual destructors}
Destructor should always be made \ttt{virtual} to ensure correct behaviour if 
the class is eventually derived from. This rule does not apply if a class 
is made \ttt{final}, of course.

\section{Inlining}
One line methods should be inlined to ensure correct optimization at compile 
time. If a method has more than one line, do not inline! Example:
\includecode{\functionsSnippets inlining.cpp}

Prefer \ttt{inline} to MACROs, whenever possible. This avoid tricky copy and 
paste errors which may be hard to find:
\includecode{\functionsSnippets inlineVsMacros.cpp}